NFC and burnout in teachers - A replication and extension study

### 2021-09-01 Manuscript/Manuscript.Rmd
added plot for fit2
added labels to plot

>>>>

  # Plot

  fit2_plot <- semPaths(fit2, what = "par",
                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","ee","dp","rpe","NFC","DTH","DTL","DRF","MBI"),
                        layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-1,-0.8,-0.6,-0.2,0,0.2,0.6,0.8,1,0.6,0.8,1,-0.8,-0.8,0,0.8,0.8,
                                                 -1,-1,-1,-1,1,1,1,1,1,1,1,1,1,-1,-1,-1,-0.5,0.5,0.5,0.5,-0.5),
                                        nrow = 21, ncol = 2))
